% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer



%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
 \let\cleardoublepage\relax
 \let\cleardoublepage\relax

\chapter*{Acknowledgements} % Acknowledgements section text

I have been lucky to work and collaborate with some incredible colleagues during my PhD. I would like to thank my supervisor Prof. Mauro Ferriera for his guidance and patience over the past four years. To my co-supervisor Prof. Claudia Gomes da Rocha, I am truly grateful for your advice and insights during the PhD. Our brainstorming sessions in Mauro's office were the most enjoyable aspects of my PhD, and I will cherish those memories. I would like to thank my collaborators, in particular Prof. John Boland, Dr. Hugh Manning, and Fabio Niosi. Group meetings were always a source of new and exciting ideas.

On a personal note, I would like to thank my friends who have always been a source of support, encouragement, and distraction. I would not be where I am today if not for the constant love and support of my family. To my parents, I am truly grateful for your unbounded encouragement and guidance. To my siblings, grandparents, aunts, uncles and cousins, thank you all for your moral support. To Laura, your love has been an immense support. Always there to listen and laugh, this work would not have been possible without you.
% \begin{flushright}
% { \slshape Contemplate the danger of a man who thinks only of himself. }\\
% ---Yukio Mishima 
% \end{flushright}

\endgroup
