% Publications - a page listing research articles written using content in the thesis

\pdfbookmark[1]{Publications}{Publications} % Bookmark name visible in a PDF viewer

\chapter*{Publications} % Publications page text

Publications resulting, partially or wholly, from this work:
\bigskip

\begin{itemize}
 \item[-] H. G. Manning, C. G. Rocha, \textbf{C. O'Callaghan}, M. S. Ferreira, J. J. Boland \\
 \emph{Predicting the Performance and Optimization of Transparent Conducting Ag Nanowire Networks} \\ 
 In preperation, 2018.
\end{itemize}


\begin{itemize}
 \item[-] \textbf{C. O'Callaghan}, C. G. Rocha, H. G. Manning, F. Niosi, J. J. Boland, and M. S. Ferreira. \\
 \emph{Self-Similar and Neuromorphic Properties in Core-Shell Nanowire Network Systems} \\ 
 Conference Proceedings, IEEE Nano Conference, 2018.
\end{itemize}

\begin{itemize}
 \item[-] \textbf{C. O'Callaghan}, C. G. Rocha, F. Niosi, H. G. Manning, J. J. Boland, and M. S. Ferreira. \\
 \emph{Collective Capacitive and Memristive Responses in Random Nanowire Networks: Emergence of Critical Connectivity Pathways} \\ 
 Accepted for Publication, Journal of Applied Physics, 2018.
\end{itemize}

\begin{itemize}
 \item[-] H. G. Manning, F. Niosi, C. G. Rocha, A. T. Bellew, \textbf{C. O'Callaghan}, S. Biswas, P. Flowers, B. J. Wiley, J. D. Holmes, M. S. Ferreira, J. J. Boland. \\
 \emph{Emergence of Winner-takes-all Connectivity Paths in Random Nanowire Networks} \\ 
Nature Communications 9, 3219, 2018.
\end{itemize}

\begin{itemize}
 \item[-] J. Jadwiszczak, \textbf{C. O'Callaghan}, Y. Zhou, D. S. Fox, E. Weitz, D. Keane, C. P. Cullen, I. O'Reilly, C. Downing, A. Shmeliov, P. Maguire, J. J. Gough, C. McGuinness, M. S. Ferreira, L. Bradley, J. J. Boland, G. S. Duesberg, V. Nicolosi, H. Zhang. \\
 \emph{Oxide-Mediated Recovery of Field-Effect Mobility in Plasma-Treated MoS$_2$} \\ 
 Science advances 4, eaao5031, 2018.
\end{itemize}

\begin{itemize}
 \item[-] \textbf{C. O'Callaghan}, C. G. da Rocha, H. G. Manning, J. J. Boland, and M. S. Ferreira.\\
 \emph{Effective Medium Theory for the Conductivity of Disordered Metallic Nanowire Networks} \\ 
 Physical Chemistry Chemical Physics, 18,27564-27571, 2016.
\end{itemize}

\begin{itemize}
 \item[-] J. A. Fairfield, C. G. Rocha, \textbf{C. O'Callaghan}, M. S. Ferreira, J. J. Boland. \\
 \emph{Co-Percolation to Tune Conductive Behaviour in Dynamical Metallic Nanowire Networks} \\ 
 Nanoscale 8 (43), 18516-18523, 2016.
\end{itemize}

\begin{itemize}
 \item[-] C. G. Rocha, H. G. Manning, \textbf{C. O'Callaghan}, C. Ritter, A. T. Bellew, J. J. Boland, M. S. Ferreira. \\
 \emph{Ultimate Conductivity Performance in Metallic Nanowire Networks} \\ 
 Nanoscale 7 (30), 13011-13016, 2015.
\end{itemize}

